\cvsection{Experience}
\begin{cventries}
  \cventry
    {Developer Relations Engineer}
    {\href{http://www.sourced.tech/}{Source\{d\}}}
    {Madrid, Spain}
    {Jul. 2016 - Currently}
    {
      Source\{d\} is a technology-driven product addressing the challenge of analyzing the world's open source code. We analyze more than 16m GitHub projects with 900m code contributions across 6mm+ developers.\vspace{4mm}
      \begin{cvitems}
      \item {Alongside a team of engineers, I was tasked with the process of identifying, qualifying and presenting developers across diverse technology backgrounds, such as web development, infrastructure, mobile, and DevOps, to our extensive client base.} 
      \item {I was responsible for managing backend, infrastructure, and DevOps-related positions.}
      \item {I managed and kept contact with CTOs of companies such as Runtastic, Heetch, Accenture, and Zenly.}
      \item {I participated on a mentoring program in order to strengthen my programming skills, focusing on Go language.}
      \end{cvitems}
    }
  \cventry
    {Test Engineer}
    {\href{http://www.techonrails.com/}{MNI Tech On Rails}}
    {Madrid, Spain}
    {Mar. 2016 - Jun. 2016}
    {
      Tech on Rails is an engineering and technology consultancy specialized in railway, aerospace and energy. We collaborated with our customers to develop and adapt engineering products or solutions to a specific project, customer or market.\vspace{4mm}
      \begin{cvitems}
        \item {I participated in systems engineering, product design, development, integration and testing.}
        \item {I used advanced software tooling for technical solutions and engineering teams.}
        \item {I developed and implemented unit and integration testing routines for railway automation and safety systems.}
      \end{cvitems}
    }
  \cventry
    {Development and Support Engineer}
    {\href{http://www.alter-info.com/}{Alterinfo}}
    {Caracas, Venezuela}
    {May 2015 - Oct. 2015}
    {
    Alterinfo is a technology company, incubated by Sartenejas Technological Park, focused on developing high-performance equipment for building and scaling the best technical solution to its customers.\vspace{4mm}
      \begin{cvitems}
        \item {Alongside a team of young engineers, I was responsible for the design, construction and installation of a junction box for interfacing navigation modules, inertial platforms and energy systems, on board of S31 and S32, class U209 submarines, for the Venezuelan Army, through Sagem Défense Sécurité.}
        \item {I also participated in the development of multiple products based on proprietary technologies and embedded systems, mainly National Instruments software and hardware.}
      \end{cvitems} 
    }
  \cventry
    {Researcher}
    {{\href{http://www.labc.usb.ve/mecatronica/}{Mechatronics Team, Simón Bolívar University}}}
    {Sartenejas, Venezuela}
    {Sep. 2014 - Mar. 2015}
    {
    The Mechatronics Research and Development Team is a branch of Sim\'on Bol\'ivar University dedicated to developing solutions based on control systems, automation, computer science, artificial intelligence, mechanics and electronics.\vspace{4mm}
      \begin{cvitems}
        \item {Tasked with the design and implementation of a Wireless Sensor Network, built around the Raspberry Pi SoC micro-computer, for monitoring and data analysis of climatic conditions across the University's grounds.}
        \item {Performed research, programming and testing of the entire system, implemented in Python.}
      \end{cvitems}
    }
\end{cventries}
